### 2017-04-06 paper/modes.tex
clarifying configuration modes

The list below shows the choices to control parallelism within one
Java Virtual Machine (JVM), which runs in a single CPU process.  These
options are offered by the testing framework, \eg{}, JUnit.

@@

The list below shows the choices to control parallelism through the
build system, \eg{}, Maven.  The build system can spawn multiple JVMs,
each running on its own OS process on a given CPU and handling a
partition of the test set.

\begin{itemize}
\item
    \textbf{Forked classes; sequential methods (\ForkSeq).}~This
    configuration spawns multiple JVMs, assigning a partition of the
    test set to each JVM.  Test methods run sequentially within each
    JVM.
\item
    \textbf{Forked classes; parallel methods (\ForkParMeth).}~In
    addition to forking multiple JVMs, as \ForkSeq{} does, this
    configuration runs tests concurrently, as \SeqClassParMeth{} does.
\end{itemize}

@@

Forking OS processes to run test jobs is a popular mechanism of build
systems to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based build systems, such as Maven
and Ant, this amounts to spawning one JVM instance to handle a test
job and aggregating corresponding results when test jobs finish.  Note
that forking can only be combined with configuration
\SeqClassParMeth{} (see Section~\ref{sec:frameworks}) as Maven only
accepts one test class at a time per forked process.  To attenuate the
non-trivial cost of spawning new JVM processes on every test class,
Maven offers an option to reuse the JVM.

@@

\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
Maven implements this feature through its JUnit test plugin
Surefire~\cite{maven-surefire-plugin}.  With this configuration, Maven
forks one JVM per core (\CodeIn{forkCount} parameter) and uses five
threads (\CodeIn{threadCount} parameter) to run test methods
(\CodeIn{parallel} parameter) within each forked JVM.  Maven reuses
created JVMs on subsequent forks when execution of a test class
terminates (\CodeIn{reuseFork} parameter).

>>>>

The list below shows the choices to control parallelism within one
Java Virtual Machine (JVM).  These options are offered by the testing
framework (\eg{}, JUnit).

@@

%% The build system can spawn multiple JVMs, each running on its own OS
%% process on a given CPU and handling a partition of the test set.

Forking OS processes to run test jobs is the basic mechanism of build
systems to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based build systems, such as Maven
and Ant, this amounts to spawning one JVM, on a given CPU, to handle a
test job and aggregating results when jobs finish.  The list below
shows the choices to control parallelism through the build system
(\eg{}, Maven).

\begin{itemize}
\item
    \textbf{Forked JVMs with sequential methods (\ForkSeq).}~The build
    system spawns multiple JVMs with this configuration, assigning a
    partition of the set of test classes to each JVM.  Test methods
    run sequentially within each JVM.
\item
    \textbf{Forked JVMs with parallel methods (\ForkParMeth).}~With
    this configuration, the build system forks multiple JVMs, as
    \ForkSeq{} does.  However, it runs tests concurrently, as
    \SeqClassParMeth{} does.
\end{itemize}

@@

Note from the listing that forking can only be combined with
configuration \SeqClassParMeth{} (see Section~\ref{sec:frameworks}) as
Maven made the design choice to only accept one test class at a time
per forked process.  Maven offers an option to reuse JVMs that can be
used to attenuate the potentially high cost of spawning new JVM
processes on every test class (if reuse is enabled) and also to
achieve test isolation (if reuse is disabled).

@@

\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
Maven implements this feature through its Surefire JUnit test
plugin~\cite{maven-surefire-plugin}.  With this configuration, Maven
forks one JVM per core (\CodeIn{forkCount} parameter) and uses five
threads (\CodeIn{threadCount} parameter) to run test methods
(\CodeIn{parallel} parameter) within each forked JVM.  Maven reuses
created JVMs on subsequent forks when execution of a test class
terminates (\CodeIn{reuseFork} parameter).
